Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-08-01 doc/PRF2022/PRF_main.tex
worked on revisions

\begin{abstract}
  Active colloidal systems with non-equilibrium self-organization
  is a long-standing challenging area in biology.
  To understand how hydrodynamic flow may be used to actively
  control self-assembly of Janus particles (JPs), we use a model
  recently developed for the many-body hydrodynamics of amphiphilic
  JPs suspended in a viscous background flow (JFM, 941, 2022).
  We investigate how various bilayer structures arise from tuning
  the hydrophobic properties of the JP-solvent interface.
  Focusing on a simple tuning of the hydrophobicity distribution,
  we found
  JPs assembled into uni-lamella, multi-lamella and striated
  structures.  To introduce dynamics, we include a linear shear flow and a
  Taylor-Green mixing flow, and measure the
  collective dynamics of JP particles in terms of their 
  (a) free energy from the hydrophobic interactions between the JPs,
  (b) order parameter for the ordering of JPs in terms of alignment of their directors, 
  and (c) strain parameter that captures the deformation in the assembly.
  We characterized the effective material properties of the JP structures
  and found that the uni-lamellar structures increases orientation order under
  shear flow, the multilamellar structure behaves as a shear thinning fluid,
  and the striated structure possesses a finite yield stress.  
  These numerical result provide insights into dynamic control of
  non-equilibrium active biological systems with similar self-organization.
% insert abstract here
\end{abstract}

@@

\begin{figure}
  \begin{center}
   \includegraphics[width=1.0\textwidth]{Figures/Figure3.pdf}
  \end{center}
  \caption{
    \label{fig:BC1_shear}
    Panels (a)-(c) are a snapshot at $t=0.5\ \mu$s of the multiple-component bilayer
    with shear rate $\dot \gamma = \{0.05, 0.075, 0.1\}$.
    The initial configuration is shown in inset of panel (a).
    The streamlines are plotted in the background.
    Panel (d) plots the free energies,
    panel (e) shows the orientational parameter $\tilde{S}_2$,
    and panel (f) shows positional parameter E.
}
\end{figure}

@@

%%%
\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure4.pdf}
  \end{center}
  \caption{
    \label{fig:Ves_shear}
A single vesicle in a shear flow. Panels (a)--(c) are snapshots for
  $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=0.16\ \mu$s where the
  pre-relaxed initial configuration is shown in inset of panel (a).  The
  streamlines are plotted in the background.  Panel (d) plots the free
  energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel
  (f) shows positional parameter E.
     }
\end{figure}
\citet{Fu2022_JFM} studied the hydrodynamics of a JP vesicle under a
linear shear flow. Focusing on drawing analogies to hydrodynamics of a
vesicle in continuum modeling (such as
tank-treading~\cite{keller_skalak_1982,Finken08,Shaqfeh11}, bilayer
slip~\cite{sch-vla-mik2010,denOtter2007,Zgorski2019}, and
permeability~\cite{chabanon2017, qua-gan-you2021}), our previous studies
showed the existence of a critical shear rate above which the JP vesicle
ruptures~\cite{grandmaison_brancherie_salsac_2021,D2SM00179A}. Based on
the these early results, we reinitialized the BC (i) configuration in
the form of a single, circular vesicle (rather than several bilayer
components) and illustrate how the three measures of structural
deformation correlate to the dynamics of a JP vesicle.

@@

%%%%%%%
%
\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC1_TG} Multiple component bilayers in a
  Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \mu$s. The
  pre-relaxed initial configuration is shown in the inset of panel (a).
  The streamlines are plotted in the background. Panel (d) plots the
  free energies; panel (e) shows the orientational parameter
  $\tilde{S}_2$; panel (f) shows the positional parameter $E$.}
\end{figure}
%
\subsection{Bilayer and vesicle configurations in a Taylor-Green flow}
Next, we subject the JP structures to the Taylor-Green (TG) background
flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty(\xx) = V_0\; \frac{\text{nm}}{\text{ns}}\;
\left(
-\cos\left(x/\lambda\right)
 \sin\left(y/\lambda\right)
         {\bf e}_x
         +\sin\left(x/\lambda\right)
         \cos\left(y/\lambda\right)
             {\bf e}_y\right),
\end{equation}
where $x = {\bf e}_x \cdot \xx$ and $y = {\bf e}_y \cdot \xx$
are the horizontal and vertical coordinates, respectively. 
The TG flow is a confining flow consisting of a checkerboard pattern
of cells with alternating circulation. We control the flow by the
dimensionless flow strength $V_0$ and the dimensionless cell size $l$
defining $\lambda = l$ nm. For most of the results in this subsection,
we use the parameter $l=2$.
%

\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
  \end{center}
\caption{\label{fig:ves_TG} Single vesicle in a TG flow. Panels (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a). The streamlines are plotted in the background.
Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
}
\end{figure}

There is no appreciable pattern in the deformation for the multicomponent bilayer case in TG flow. 
Figure~\ref{fig:BC1_TG}(a)--(c) are the snapshots when $V_0=0.1,0.15,0.2$ at $t = 0.2$ $\upmu$s.
At all flow strengths, the bilayer components are separated and mixed by the flow in neighboring cells. 
In the $V_0 = 0.2$ case, the flow breaks off components consisting of only a few particles,
leading an increase in energy (Figure~\ref{fig:BC1_TG}(d), long dashed curve).
There is no significant change in the orientational order.  There is an initial increase in the
strain parameter due to component mixing, but the strains remains bounded since the particles
stay confined to within the neighbors of the central cell.

Patterns in the deformation, however, do emerge in the case of a vesicle in TG flow.
For a vesicle in a Taylor-Green flow, Figure~\ref{fig:ves_TG}(a)--(c) are configurations at $t=0.2\  \mu$s where $V_0=0.1,0.15,0.2$.
Here, the circular vesicle takes on a steady square shape for moderate flow rates $V_0 = 0.1$ and $V_0 = 0.15$.
In these cases, there is little change in the vesicle free energy and
order (Figure~\ref{fig:ves_TG}(d)-(f))).
The vesicle disintegrates for $V_0 = 0.2$, leading to a jump in energy, drop in order, and increase in strain,
suggesting that the vesicle has a critical TG flow strength in the interval $[0.15, 0.2]$ separating the
intact and ruptured end-states.

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure7.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BTG_Scale} With $V_0=0.1$, panels (a)-(d) show the configurations with streamlines when a vesicle is in Taylor-Green flow at $t=1 \mu$s and $l= 1,2,3,4$, respectively.
  For panel (e), the enclosed area $A_0/A$ calculated from the bilayer midplane decreases over time and the total length (as shown in the inset) measured from the midplane remains nearly constant with small magnitude of oscillations.
  }
\end{figure}

The vesicle shape is also tied to cell size $l$.  
Figure~\ref{fig:BTG_Scale}(a)--(d) show the deformation of a vesicle in a
TG flow for $V_0=0.1$ when $t = 1$ $\upmu$s.  
For the smallest cell size $l = 1$ tested, the vesicle is somewhat octagonal
and passes through multiple cells (Figure~\ref{fig:BTG_Scale}(a)).
For the largest cell size $l = 4$,
the vesicle is rhomboid and surrounds a single cell.

@@

We calculated the vesicle area $A$ and length $L$ (initial area $A_0$, initial length $L_0$)
by averaging the area/length for the inner and outer leaflets.  
As shown in Figure~\ref{fig:BTG_Scale}(e),
the relative area $A/A_0$ decreases during the simulations, with a rate
depending nonmonotonically on $l$.  
The relative length $L/L_0$, however, is constant in $t$ for all cell
sizes (Figure~\ref{fig:BTG_Scale}(e), inset).
This implies that the vesicle behaves as an inextensible, permeable membrane.
In previous work, \cite{Fu2022_JFM} determined the permeability constant of particle-based vesicles
in the context of shear background flow\cite{chabanon2017,qua-gan-you2021}.

%%%
\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure8.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC2_shear}
Multilamellar structure in a shear flow. Panels (a)-(c) are snapshots for $\dot \gamma = \{0.05, 0.1, 0.15\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a). The streamlines are plotted in the background.
Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
       }
\end{figure}

\subsection{Multilamellar and striated configurations in shear and TG flow}
We have simulated particles for the multilamellar (BC (ii)) and striated (BC (iii))
boundary conditions, in both shear and TG background flow.  The results are
qualitatively similar and will be presented in tandem. 
For the multilamellar case, we place a 60-particle configuration (inset
of Figure~\ref{fig:BC2_shear}(a))
in shear flows with $\dot\gamma=0.05, 0.1, 0.15$ and in TG flow with flow rates $V_0=0.1, 0.15, 0.2$.
For the striated case, we also place a 60-particle configuration (inset
of Figure~\ref{fig:BC3_shear}(a))
in shear and TG background flows.  Here, somewhat larger rates are required to see appreciable
deformations for this boundary condition: $\dot\gamma=0.1, 0.125, 0.15$
and $V_0=0.2, 0.25, 0.3$ respectively.

In terms of shear flow, the free energies are steady at the lowest shear 
rates (Figure~\ref{fig:BC2_shear}(d), Figure~\ref{fig:BC3_shear}(d)).
The free energy of the striated configuration oscillates by $\pm 1$ $\mathrm{k_BT}$/nm
due to square reference region deforming into a rhomboidal shape under shear
flow (Figure~\ref{fig:BC3_shear}(d), solid curve).  No such oscillation
is present in for the multilamellar configuration since this shape is circularly
isotropic (Figure~\ref{fig:BC2_shear}(d), solid curve).
At the lowest shear rates, there is, however, oscillation in the strains
of both configurations, 
while the order parameter $\tilde S_2$ is more less constant
(Figure~\ref{fig:BC2_shear}(e),(f), Figure~\ref{fig:BC3_shear}(e),(f), solid curves).
In summary, both multilallar and striated configurations behave as nearly
rigid bodies under shear flow when the shear rate $\dot \gamma$ is low.

In the high shear rate cases ($\dot\gamma=0.15$), both the
multilamellar and striated configurations become disordered.  For BC (ii),
the lamella break apart so that individual bilayers are no longer discernible
(Figure~\ref{fig:BC2_shear}(c)).
For BC (iii), the stria peal away from the main body,
but remain individually intact (Figure~\ref{fig:BC3_shear}(c)).  
Overall, the particles in BC (ii) and BC (iii) remain bounded
and do not drift away in the shear background flow like for the
BC (i) boundary condition (Figure~\ref{fig:BC1_shear}(c),
Figure~\ref{fig:Ves_shear}(c)).

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure9.pdf}    
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC2_TG} 
Multilamellar structure in a Taylor-Green flow. Panels (a)-(c) are snapshots for $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a). The streamlines are plotted in the background.
Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
 }
\end{figure}

@@

At large flow rates $V_0$, both configurations depart significantly from their local
equilibrium.  The lamella bilayers from BC (ii) break apart, forming several,
unlayered bilayer components (Figure~\ref{fig:BC2_TG}(c)).
In BC (iii), the stria also break apart, but neighboring particles form
'X'-like arrangements (Figure~\ref{fig:BC3_TG}(d)), resembling the doubly alternating
director equilibrium (Figure~\ref{fig:relax}(d), center, top white rectangle).

@@

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure10.pdf}        
  \end{center}
      \caption{\label{fig:BC3_shear}  A striated configuration in a shear flow. Panels (a)-(c) are snapshots for $\dot \gamma = \{0.1, 0.125, 0.15\}$ at $t=0.1\mu$s where the pre-relaxed initial configuration is shown in inset of panel (a). The streamlines are plotted in the background.
Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
    }
\end{figure}

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure11.pdf}            
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC3_TG} A striated configuration in a Taylor-Green flow. Panels (a)-(c) are snapshots for $V_0=\{0.2, 0.25, 0.3\}$ at $t=0.4\mu$s where the pre-relaxed initial configuration is shown in inset of panel (a). The streamlines are plotted in the background.
Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
}
\end{figure}

\section{Discussion}
Our results were for $N_b = 60$.  This particle number was large enough for the JP to form
measurable structures while giving manageable simulation times (days) on a single computing processor.
The simulation time for $N_b = 198$ in Figure~\ref{fig:relax} and Fig. \ref{fig:relax_energy}
was several weeks, and so we avoided simulations of this size for our results.
We used $N = 16$ grid points per particles for all simulations.  We performed a convergence study
and found that using $N = 16$ or $N = 24$ grid points per particle gave quantitatively indistinguishable
results.  The time courses consisted of $O(10^3)$ time steps with $\Delta t = 0.2$ nm.

The free energy $F$ defined in \eqref{eq:free_energy}
scales with the boundary data $g$ and repulsion modulus $M$.
To remove the degree of freedom in the boundary data,
we scaled all boundary data so that the square integral of $g$ is independent of
type of boundary condition; BC (i), (ii), or (iii).
This way, for a fixed configuration, the hydrophobic interaction portion of the
free energy (the integral in \eqref{eq:free_energy}) converges to $2\pi \gamma c N_b$
in the limit $\rho = 0$.  This gives a free energy per particle that is independent
of the shape/intensity of the hydrophobic interface.  In practice, $\rho > 0$ is fixed
and the JP assume different configurations.  As a result, the equilibrium energies
per particle in our simulations are different and depend on the boundary condition
(Figure~\ref{fig:relax_energy}).
They are about 0.26 $\mathrm{k_BT}$/nm for BC (ii),
0.55 $\mathrm{k_BT}$/nm for BC (i), and
1.4 $\mathrm{k_BT}$/nm for BC (iii).

Next, we suspended JP in viscous background flows and observed deformations
as a function of flow strength.  There were three categories of boundary
conditions; BC (i), BC (ii), and BC (iii); that formed bilayer, multilamellar, and striated
configurations, respectively. For BC (i), we considered both an unstructured bilayer
and a vesicle bilayer.  The background flows were a linear shear flow and a Taylor-Green (TG) flow.

We can characterize the effective material properties of the JP structures
based on the changes in free energy, orientationl order, and strain as a function
of flow strength.
Generally, $F$ increases, $\tilde S_2$ decreases, and 
$E$ increases with increases in both $\dot \gamma$ and $V_0$, as expected.
Structurally, the striated JP configuration for BC (iii) behaved the most
like a rigid body over the flow strengths tested.  For this structure,
the deformations measures were constant in time for shear rates $\dot \gamma$ up to
$0.15$ and TG flow rate $V_0$ up to $0.25$
(Figure~\ref{fig:BC3_shear} and Figure~\ref{fig:BC3_TG}).
Conversely, a $25 - 50 \%$
smaller value for $\dot \gamma$ or $V_0$ were required to observe
nonrigid deformations for the BC (i) and BC (ii) cases.

In terms of fluid behavior,
the multilamellar (BC (ii)) structure behaves as shear thinning fluid
while the striated structure (BC (iii)) has a finite yield stress. 
Qualitatively, the strains for BC (ii) increases gradually 
with shear rate (Figure~\ref{fig:BC2_shear}(f)).
In contrast, the strains for BC (iii) are constant over a range of flow strengths
and then increase when the flow strengths are large enough
to deform the body (Figure~\ref{fig:BC3_shear}(f)).
To quantify this behavior, we form 
\[
\mu_{\text{hyd}} = \frac{\dot \gamma}{\dot E} \mu
\]
as an effective dynamic viscosity of the particle assemblies.
The numerator $\dot \gamma \mu$ gives the force per
area provided by the solvent stresses where
$\mu = 1$ mPa s is
the solvent viscosity.
The strain rate $\dot E$ of the body is the slope of a linear fit to the strain curves e.g.,
in Figure~\ref{fig:BC2_shear}(f).

>>>>

\begin{abstract}
  Active colloidal systems with non-equilibrium self-organization is a
  long-standing challenging area in biology. To understand how
  hydrodynamic flow may be used to actively control self-assembly of
  Janus particles (JPs), we use a model recently developed for the
  many-body hydrodynamics of amphiphilic JPs suspended in a viscous
  background flow (JFM, 941, 2022). We investigate how various bilayer
  structures arise from tuning the hydrophobic properties of the
  JP-solvent interface. Focusing on a simple tuning of the
  hydrophobicity distribution, we found JPs assembled into uni-lamella,
  multi-lamella and striated structures. To introduce dynamics, we
  include a linear shear flow and a Taylor-Green mixing flow, and
  measure the collective dynamics of JP particles in terms of their (a)
  free energy from the hydrophobic interactions between the JPs, (b)
  order parameter for the ordering of JPs in terms of alignment of their
  directors, and (c) strain parameter that captures the deformation in
  the assembly. We characterized the effective material properties of
  the JP structures and found that the uni-lamellar structures increases
  orientation order under shear flow, the multilamellar structure
  behaves as a shear thinning fluid, and the striated structure
  possesses a finite yield stress. These numerical result provide
  insights into dynamic control of non-equilibrium active biological
  systems with similar self-organization.
\end{abstract}

@@

\begin{figure}
  \begin{center}
   \includegraphics[width=1.0\textwidth]{Figures/Figure3.pdf}
  \end{center}
  \caption{
    \label{fig:BC1_shear}
    Panels (a)--(c) are a snapshot at $t=0.5\ \mu$s of the
    multiple-component bilayer with shear rate $\dot \gamma = \{0.05,
    0.075, 0.1\}$. The initial configuration is shown in inset of panel
    (a). The streamlines are plotted in the background. Panel (d) shows
    the free energies, panel (e) shows the orientational parameter
    $\tilde{S}_2$, and panel (f) shows positional parameter E.}
\end{figure}

@@

%%%
\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure4.pdf}
  \end{center}
  \caption{
    \label{fig:Ves_shear}
A single vesicle in a shear flow. Panels (a)--(c) are snapshots for
  $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=0.16\ \mu$s where the
  pre-relaxed initial configuration is shown in inset of panel (a). The
  streamlines are plotted in the background. Panel (d) shows the free
  energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel
  (f) shows positional parameter E.}
\end{figure}
\citet{Fu2022_JFM} studied the hydrodynamics of a JP vesicle under a
linear shear flow. Focusing on drawing analogies to hydrodynamics of a
vesicle in continuum modeling (such as
tank-treading~\cite{keller_skalak_1982,Finken08,Shaqfeh11}, bilayer
slip~\cite{sch-vla-mik2010,denOtter2007,Zgorski2019}, and
permeability~\cite{chabanon2017, qua-gan-you2021}), our previous studies
showed the existence of a critical shear rate above which the JP vesicle
ruptures~\cite{grandmaison_brancherie_salsac_2021,D2SM00179A}. Based on
the these early results, we reinitialized the BC (i) configuration in
the form of a single, circular vesicle (rather than several bilayer
components) and illustrate how the three measures of structural
deformation correlate to the dynamics of a JP vesicle.

@@

%%%%%%%
%
\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC1_TG} Multiple component bilayers in a
  Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \mu$s. The
  pre-relaxed initial configuration is shown in the inset of panel (a).
  The streamlines are plotted in the background. Panel (d) shows the
  free energies; panel (e) shows the orientational parameter
  $\tilde{S}_2$; panel (f) shows the positional parameter $E$.}
\end{figure}
%
\subsection{Bilayer and vesicle configurations in a Taylor-Green flow}
Next, we subject the JP structures to the Taylor-Green (TG) background
flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty(\xx) = V_0\; \frac{\text{nm}}{\text{ns}}\;
\left(
-\cos\left(x/\lambda\right)
 \sin\left(y/\lambda\right)
         {\bf e}_x
         +\sin\left(x/\lambda\right)
         \cos\left(y/\lambda\right)
             {\bf e}_y\right),
\end{equation}
where $x = {\bf e}_x \cdot \xx$ and $y = {\bf e}_y \cdot \xx$
are the horizontal and vertical coordinates, respectively. 
The TG flow is a confining flow consisting of a checkerboard pattern
of cells with alternating circulation. We control the flow by the
dimensionless flow strength $V_0$ and the dimensionless cell size $l$
defining $\lambda = l$ nm. For most of the results in this subsection,
we use the parameter $l=2$.
%

\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
  \end{center}
\caption{\label{fig:ves_TG} A single vesicle in a TG flow. Panels
  (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s
  where the pre-relaxed initial configuration is shown in inset of panel
  (a). The streamlines are plotted in the background. Panel (d) shows
  the free energies; panel (e) shows orientational parameter
  $\tilde{S}_2$; panel (f) shows positional parameter E.}
\end{figure}

There is no appreciable pattern in the deformation for the
multicomponent bilayer case in TG flow. Figure~\ref{fig:BC1_TG}(a)--(c)
are the snapshots when $V_0=0.1,0.15,0.2$ at $t = 0.2$ $\upmu$s. At all
flow strengths, the bilayer components are separated and mixed by the
flow in neighboring cells. In the $V_0 = 0.2$ case, the flow breaks off
components consisting of only a few particles, leading an increase in
energy (Figure~\ref{fig:BC1_TG}(d), long dashed curve). There is no
significant change in the orientational order. There is an initial
increase in the strain parameter due to component mixing, but the
strains remains bounded since the particles stay confined to the
neighbors of the central cell.

Patterns in the deformation, however, do emerge in the case of a vesicle
in TG flow. For a vesicle in a Taylor-Green flow,
Figure~\ref{fig:ves_TG}(a)--(c) are configurations at $t=0.2\ \mu$s
where $V_0=0.1,0.15,0.2$. Here, the circular vesicle takes on a steady
square shape for moderate flow rates $V_0 = 0.1$ and $V_0 = 0.15$. In
these cases, there is little change in the vesicle free energy and order
(Figure~\ref{fig:ves_TG}(d)--(f)). The vesicle disintegrates for $V_0 =
0.2$, leading to a jump in energy, drop in order, and increase in
strain, suggesting that the vesicle has a critical TG flow strength in
the interval $[0.15, 0.2]$ separating the intact and ruptured
end-states.

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure7.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BTG_Scale} With $V_0=0.1$, panels (a)--(d) show
  the configurations with streamlines of a vesicle is in a TG flow at
  $t=1 \mu$s with $l= 1,2,3,4$, respectively. In panel (e), the enclosed
  area $A_0/A$ calculated from the bilayer midplane decreases over time
  and the total length (shown in the inset) measured from the midplane
  remains nearly constant with small magnitude of oscillations.}
\end{figure}

The vesicle shape is also related to the cell size $l$.
Figure~\ref{fig:BTG_Scale}(a)--(d) show the deformation of a vesicle in
a TG flow for $V_0=0.1$ when $t = 1$ $\upmu$s. For the smallest cell
size $l = 1$ tested, the vesicle is somewhat octagonal and passes
through multiple cells (Figure~\ref{fig:BTG_Scale}(a)). For the largest
cell size $l = 4$, the vesicle is rhomboid and surrounds a single cell.

@@

We calculate the vesicle area $A$ and length $L$ (initial area $A_0$,
initial length $L_0$) by averaging the area and length of the inner and
outer leaflets. As shown in Figure~\ref{fig:BTG_Scale}(e), the relative
area $A/A_0$ decreases during the simulations, with the rate depending
nonmonotonically on $l$. The relative length $L/L_0$, however, is
constant in $t$ for all cell sizes (Figure~\ref{fig:BTG_Scale}(e),
inset). This implies that the vesicle behaves as an inextensible,
permeable membrane. In previous work, \citet{Fu2022_JFM} determined the
permeability constant of particle-based vesicles in the context of shear
background flow~\cite{chabanon2017, qua-gan-you2021}.

%%%
\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure8.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC2_shear} A multilamellar structure in a shear
  flow. Panels (a)--(c) are snapshots for $\dot \gamma = \{0.05, 0.1,
  0.15\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration
  is shown in inset of panel (a). The streamlines are plotted in the
  background. Panel (d) shows the free energies; panel (e) shows
  orientational parameter $\tilde{S}_2$; panel (f) shows positional
  parameter E.}
\end{figure}

\subsection{Multilamellar and striated configurations in shear and TG flow}
We have simulated particles for the multilamellar (BC (ii)) and striated
(BC (iii)) boundary conditions, in both shear and TG background flow.
The results are qualitatively similar and will be presented in tandem.
For the multilamellar case, we place a 60-particle configuration (inset
of Figure~\ref{fig:BC2_shear}(a)) in shear flows with $\dot\gamma=0.05,
0.1, 0.15$ and in TG flow with flow rates $V_0=0.1, 0.15, 0.2$. For the
striated case, we also place a 60-particle configuration (inset of
Figure~\ref{fig:BC3_shear}(a)) in shear and TG background flows. Here,
somewhat larger rates are required to see appreciable deformations for
this boundary condition: $\dot\gamma=0.1, 0.125, 0.15$ and $V_0=0.2,
0.25, 0.3$, respectively.

In terms of shear flow, the free energies are steady at the lowest shear
rates (Figure~\ref{fig:BC2_shear}(d), Figure~\ref{fig:BC3_shear}(d)).
The free energy of the striated configuration oscillates by $\pm 1$
$\mathrm{k_BT}$/nm due to a square reference region deforming into a
rhomboidal shape under shear flow (Figure~\ref{fig:BC3_shear}(d), solid
curve). No such oscillation is present for the multilamellar
configuration since this shape is circularly isotropic
(Figure~\ref{fig:BC2_shear}(d), solid curve). At the lowest shear rates,
there is, however, oscillation in the strains of both configurations,
while the order parameter $\tilde S_2$ is nearly constant
(Figure~\ref{fig:BC2_shear}(e),(f), Figure~\ref{fig:BC3_shear}(e),(f),
solid curves). In summary, both multilamellar and striated
configurations behave as nearly rigid bodies under shear flow when the
shear rate $\dot \gamma$ is low.

In the high shear rate cases ($\dot\gamma=0.15$), both the multilamellar
and striated configurations become disordered. For BC (ii), the lamella
break apart so that individual bilayers are no longer discernible
(Figure~\ref{fig:BC2_shear}(c)). For BC (iii), the stria peel away from
the main body, but remain individually intact
(Figure~\ref{fig:BC3_shear}(c)). Overall, the particles in BC (ii) and
BC (iii) remain bounded and do not drift away in the shear background
flow like for the BC (i) (Figure~\ref{fig:BC1_shear}(c),
Figure~\ref{fig:Ves_shear}(c)).

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure9.pdf} 
  \end{center}
  \vspace{-20pt}
  \caption{\label{fig:BC2_TG} A multilamellar structure in a
  Taylor-Green flow. Panels (a)-(c) are snapshots for $V_0 = \{0.1,
  0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial
  configuration is shown in inset of panel (a). The streamlines are
  plotted in the background. Panel (d) shows the free energies; panel
  (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows
  positional parameter E.}
\end{figure}

@@

At large flow rates $V_0$, both configurations depart significantly from
their local equilibrium. The lamella bilayers from BC (ii) break apart,
forming several unlayered bilayer components
(Figure~\ref{fig:BC2_TG}(c)). In BC (iii), the stria also break apart,
but neighboring particles form 'X'-like arrangements
(Figure~\ref{fig:BC3_TG}(d)), resembling the doubly alternating director
equilibrium (Figure~\ref{fig:relax}(d), center, top white rectangle).

@@

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure10.pdf}        
  \end{center}
  \caption{\label{fig:BC3_shear} A striated configuration in a shear
  flow. Panels (a)-(c) are snapshots for $\dot \gamma = \{0.1, 0.125,
  0.15\}$ at $t=0.1\mu$s where the pre-relaxed initial configuration is
  shown in inset of panel (a). The streamlines are plotted in the
  background. Panel (d) shows the free energies; panel (e) shows
  orientational parameter $\tilde{S}_2$; panel (f) shows positional
  parameter E.}
\end{figure}

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure11.pdf}            
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC3_TG} A striated configuration in a Taylor-Green
  flow. Panels (a)-(c) are snapshots for $V_0=\{0.2, 0.25, 0.3\}$ at
  $t=0.4\mu$s where the pre-relaxed initial configuration is shown in
  inset of panel (a). The streamlines are plotted in the background.
  Panel (d) shows the free energies; panel (e) shows orientational
  parameter $\tilde{S}_2$; panel (f) shows positional parameter E.}
\end{figure}

\section{Discussion}
Our results were for $N_b = 60$ particles. This particle number was
large enough for the JP to form measurable structures while giving
manageable simulation times (days) on a single computing processor. The
simulation time for $N_b = 198$ in Figure~\ref{fig:relax} and
Figure~\ref{fig:relax_energy} was several weeks, and so we avoided
simulations of this size for our results. We used $N = 16$ grid points
per particle for all simulations. We performed a convergence study and
found that using $N = 16$ or $N = 24$ grid points per particle gave
quantitatively indistinguishable results. The time courses consisted of
$O(10^3)$ time steps with $\Delta t = 0.2$ nm.

The free energy $F$ defined in~\eqref{eq:free_energy} scales with the
boundary data $g$ and repulsion modulus $M$. To remove the degree of
freedom in the boundary data, we scaled all boundary data so that the
square integral of $g$ is independent of the type of boundary condition; BC
(i), (ii), or (iii). This way, for a fixed configuration, the
hydrophobic interaction portion of the free energy (the integral
in~\eqref{eq:free_energy}) converges to $2\pi \gamma c N_b$ in the limit
$\rho = 0$. This gives a free energy per particle that is independent of
the shape and intensity of the hydrophobic interface. In practice, $\rho
> 0$ is fixed and the JPs assume different configurations. As a result,
the equilibrium energies per particle in our simulations are different
and depend on the boundary condition (Figure~\ref{fig:relax_energy}).
They are about 0.26 $\mathrm{k_BT}$/nm for BC (ii), 0.55
$\mathrm{k_BT}$/nm for BC (i), and 1.4 $\mathrm{k_BT}$/nm for BC (iii).

Next, we suspended JPs in viscous background flows and observed
deformations as a function of flow strength. There were three categories
of boundary conditions---BC (i), BC (ii), and BC (iii)---that formed
bilayer, multilamellar, and striated configurations, respectively. For
BC (i), we considered both an unstructured bilayer and a vesicle
bilayer. The background flows were a linear shear flow and a TG flow.

We can characterize the effective material properties of the JP
structures based on the changes in free energy, orientational order, and
strain as a function of flow strength. Generally, $F$ increases, $\tilde
S_2$ decreases, and $E$ increases with increases in both $\dot \gamma$
and $V_0$, as expected. Structurally, the striated JP configuration for
BC (iii) behaved the most like a rigid body over the flow strengths
tested. For this structure, the deformation measures were constant in
time for shear rates $\dot \gamma$ up to $0.15$ and TG flow rate $V_0$
up to $0.25$ (Figure~\ref{fig:BC3_shear} and Figure~\ref{fig:BC3_TG}).
Conversely, a $25--50 \%$ smaller value for $\dot \gamma$ or $V_0$ were
required to observe nonrigid deformations for the BC (i) and BC (ii)
cases.

In terms of fluid behavior, the multilamellar (BC (ii)) structure
behaves as a shear thinning fluid while the striated structure (BC (iii))
has a finite yield stress. Qualitatively, the strains for BC (ii)
increases gradually with shear rate (Figure~\ref{fig:BC2_shear}(f)). In
contrast, the strains for BC (iii) are constant over a range of flow
strengths and then increase when the flow strengths are large enough to
deform the body (Figure~\ref{fig:BC3_shear}(f)). To quantify this
behavior, we form 
\begin{align}
\mu_{\text{hyd}} = \frac{\dot \gamma}{\dot E} \mu 
\end{align}
as an effective dynamic viscosity of the particle assemblies. The
numerator $\dot \gamma \mu$ gives the force per area provided by the
solvent stresses where $\mu = 1$ mPa s is the solvent viscosity. The
strain rate $\dot E$ of the body is the slope of a linear fit to the
strain curves e.g., in Figure~\ref{fig:BC2_shear}(f).
